How Alignment Impact Language Learning Tasks? \\ A Visual Analytics Tool for Interpreting, Debugging, \\ and Tunning Text Entailment Model

### 2018-02-16 paper/paper_entailVis.tex
update paper layout

%% Abstract section.
\abstract{
In Natural Language Processs (NLP) research attention mechanism has gained a
strong following,

} % end of abstract

@@

%% the only exception to this rule is the \firstsection command
\input{intro_entailVis.tex}
\input{relatedWorks_entailVis.tex}

>>>>

%% Abstract section.
% What are we doing in this paper
\abstract{
With the advances of deep learning, neural network based models have reset
the state-of-the-art for nearly all linguistic tasks in natural language
processing. The disruptive advance also brings enormous challenges.
The opaque nature of neural network model leads to hard to debug system and
difficult to interpret mechanism~cite{}. In this work, we use textual
entailment task as an example to illustrate how a flexible visualization
system can help NLP researchers quickly identify the potential limitation of
a models and probe the model inner states for interpreting key mechanism
such as attention.
} % end of abstract

@@

%% the only exception to this rule is the \firstsection command
\input{intro_entailVis.tex}
\input{relatedWorks_entailVis.tex}
\input{background.tex}
% \input{tasks.tex}
\input{perturbation.tex} % how to do the perturbation
\input{attention.tex} % how to encode the information
\input{application.tex}
%%%%%%%%%%%%% identify errors %%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% interpret attention %%%%%%%%%%%%%%%%%%%

\input{discussion.tex} % how to encode the information
